Tables

### 2024-11-21 index.qmd
revising and editing draft. make likert tables and plots

# also load the raw data dict for comparison
raw_spss_dict <- read.csv("data/raw_spss_dict.csv")

@@

Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024]. For instance, we have witnessed many people's outright refusal to accept the 2020 U.S. election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate. Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2]. Or in other words, there is only so much that election officials can do to sustain or improve public trust in election administration.

Even though election officials can do a lot to secure election integrity, especially under intense scrutiny, there's not much they can do to cement public confidence after election night passes. At best, election officials can ease public anxieties prior to election night. As mentioned, this usually consists of enhancing procedures and practices and adapting to advancing election technology.

One point of contention that election officials have faced in the past regard evaluation of election workers. Previous literature has focused on how voter interaction with election workers [@claassen2008], or the voter experience generally [@atkeson2007], influences evaluations of election administration. As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009]. However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's perception or evaluation of their own experience as well as subsequent evaluations of the electoral process. Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election anxieties. That is to say, it is reasonable to expect that telling people *who* will be working as election staff and volunteers would ease election anxieties, therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.

In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties (e.g., concern for electoral fairness and accuracy, as well as concerns for voter safety). Results of the survey experiment support the hypothesis that emphasizing veterans as the target of election worker recruitment efforts eases pre-elections anxieties to an extent. In particular, among those who read the treatment vignette, confidence that the elections would be fair and accurate was higher in comparison. In addition, expectations of electoral fraud were lower, as were concerns for voter safety compared to those who read a control vignette. Notable is that there was a significant increase in confidence, and lower expectations of fraud, among those who believe that the 2020 election was illegitimate.

@@

Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996]. Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024]. In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections. In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007]. Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007]. These somewhat generic issues of election worker staffing, competence, and voting technology were likely mere stepping stones leading to more intense election administration issues.

In 2024, election officials made valiant efforts to boost public confidence in the fairness and accuracy of elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024]. Although polling around the time indicated that most people thought that U.S. elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical. Enhancing trustworthiness in election administration is a regular duty for election officials, but baseless allegations regarding the fairness and accuracy of the 2020 election loomed ever larger, and the fear of political violence became prominent for both election officials and the public. Safety concerns for election staff, volunteers, and voters alike only added to, and perhaps exacerbated, public concern for the integrity of election administration in the United States. Especially as the steady increase in election official turnover seems to be increasing even more [@ferrer2024].

Election anxiety was high in the lead up to the 2024 elections in the United States. Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024]. Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024]. Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023]. Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024]. A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024]. Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, engendered increased worry for the safety of voters and election workers alike.

Suffice to say, pre-election anxiety consists of more than concerns over fairness and accuracy of vote counts in light of added safety concerns. It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.

@@

Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration. At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended). Or in other words, public trust is ascertained by the extent the public perceives the institution of election administration as trustworthy.

@@

As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out[^3]. The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election. The latter is *evaluative*---a judgement discerned empirically in hindsight after the election event has occurred. The evaluative form of trust lends to inquiries interested in public opinion on regime legitimacy, satisfaction with democracy, and perceived responsiveness [@daniller2019]. This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to electoral anxieties over the institution of election administration. Not to mention that by definition, one feels anxiety over impending uncertainties located in the future[^4].

The primary interest of this study concerns *election anxieties*, which is distinguished into two categories: fairness and accuracy, and voter safety. Of course, the direction of electoral outcomes are a particular source of electoral anxiety, but only the election outcome itself can resolve any nail-biting stress over its anticipated direction. In contrast, the anxieties of interest here are able to be relaxed to some extent prior to the election given some intervention.

@@

>>>>

# also load the raw data dict for comparison
raw_spss_dict <- read.csv("data/raw_spss_dict.csv")
```

```{r}
#| label: post_processing
#| include: false

# Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###

# code to recode levels "-99" in factor vars
data <- data |> 
  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99")))

# recode factor levels 
data <- data |> 
  # use `pewmethods` to preserve order of factor levels
  mutate(across(c(q19, q20, q21, q22, q23,q24, q25, q26,
                  q30, q31, q32, q33, q34, q35, q36, q37), 
                ~pewmethods::fct_case_when(
    .x == "Not at all confident" |
      .x == "Not at all committed" ~ "Not at all",
    .x == "Not too confident" |
      .x == "Not too committed"|
      .x == "Not too concerned"|
      .x == "Somewhat unconcerned" ~ "Not that much",
    .x == "Somewhat confident" |
      .x == "Somewhat committed" ~ "Somewhat",
    .x == "Very confident" |
      .x == "Very committed" ~ "Very",
    TRUE ~ NA
  )))

@@

Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024]. For instance, we have witnessed many people's outright refusal to accept the 2020 U.S. election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate. Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2].

Even though election officials can do a lot to secure election integrity, there's not much they can do to cement public confidence after election night passes. At best, election officials can ease public anxieties prior to election night.

One point of contention that election officials have faced in the past regard evaluation of election workers. Previous literature has focused on how voter interaction with election workers [@claassen2008], or the voter experience generally [@atkeson2007], influences evaluations of election administration. As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009]. However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.

Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election anxieties. That is to say, it is reasonable to expect that telling people *who* will be working as election staff and volunteers would ease election anxieties, therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.

In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties. Results of the survey experiment support the hypothesis that emphasizing veterans as the target of election worker recruitment efforts eases pre-elections anxieties to an extent. In particular, among those in the treatment condition, confidence that the elections would be fair and accurate was higher in comparison to those in the control. In addition, expectations of electoral fraud were lower, as were concerns for voter safety compared to those who read a control vignette. Notable is that there was a significant difference in confidence, and lower expectations of fraud, among those in the treatment condition who believe that the 2020 election was illegitimate.

@@

Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996]. Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024]. In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections. In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007]. Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].

In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024]. Although polling around the time indicated that most people thought that U.S. elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.

Election anxiety was high in the lead up to the 2024 elections in the United States. Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024]. Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024]. Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023]. Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024]. A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024]. Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.

Suffice to say, pre-election anxiety consists of more than confidence in fairness and accuracy of vote counts in light of added safety concerns. It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.

@@

Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration. At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended). Or in other words, public trust is ascertained by the extent the public is confident in the administration of elections.

@@

As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out[^3]. The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election. The latter is *evaluative*---a judgement discerned empirically in hindsight after the election event has occurred. The evaluative form of trust lends to inquiries interested in public opinion on regime legitimacy, satisfaction with democracy, and perceived responsiveness [@daniller2019]. This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to electoral anxieties over the institution of election administration. Not to mention that by definition, one feels anxiety over impending uncertainties located in the future.

The primary interest of this study is public trust in election administration prior to the election, but differentiates between confidence and concern, or otherwise trust v. anxiety. The two are inversely related, at least conceptually. As such, we might also expect an inverse relationship between reported confidence and reported concern over the different aspects of electoral administration and process. Though that leads to the conceptual wrinkle that distinguishes between trust, distrust, and anxiety, which is addressed later.

*election anxieties*[^4], which is distinguished into 
two categories: fairness and accuracy, and voter safety. Of course, the direction of electoral outcomes are a particular source of electoral anxiety, but only the election outcome itself can resolve any nail-biting stress over its anticipated direction. In contrast, the anxieties of interest here are able to be relaxed to some extent prior to the election given some intervention.

@@

## Theory

### 2024-11-21 notebooks/02-tables.qmd
revising and editing draft. make likert tables and plots

## Descriptive table
```{r}
#| label: tbl-1
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

@@

```
## Crosstables

@@

# Crosstab of Q19 by treatment group
df |> 
  janitor::tabyl(group, q19, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q19') |>
  gt::gt(
    rowname_col = 'Q19',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q19') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q19. Vote Count Confidence for Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q19. How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

@@

df |> 
  janitor::tabyl(group, q21, show_na = F) |> 
  # janitor::adorn_totals("both") |> 
  janitor::adorn_percentages("row") |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |>
  janitor::adorn_ns("rear") |> 
  janitor::adorn_title("combined", 
                       row_name = "Group",
                       col_name = "Q21") |>
  # bind_rows(.id = "group_var") |>   
  gt::gt(
    rowname_col = "row_var",
    groupname_col = "group_var") |>   
  gt::cols_label(
    c('Group/Q21') ~ "Group") |>
  # gt::cols_label_with(columns = '...1', fn = ~sjlabelled::get_label(df$q5.clps)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q21. Election staff commitment to fairness and accuracy"
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q21. Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ. How committed do you think they will be to making sure the elections held this November are fair and accurate?",
    locations = gt::cells_column_spanners()) |>
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

>>>>

```{r}
#| label: post_processing
#| include: false

# Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###

# code to recode levels "-99" in factor vars
data <- data |> 
  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99")))

# recode factor levels 
data <- data |> 
  # use `pewmethods` to preserve order of factor levels
  mutate(across(c(q19, q20, q21, q22, q23,q24, q25, q26,
                  q30, q31, q32, q33, q34, q35, q36, q37), 
                ~pewmethods::fct_case_when(
    .x == "Not at all confident" |
      .x == "Not at all committed" ~ "Not at all",
    .x == "Not too confident" |
      .x == "Not too committed"|
      .x == "Not too concerned"|
      .x == "Somewhat unconcerned" ~ "Not that much",
    .x == "Somewhat confident" |
      .x == "Somewhat committed" ~ "Somewhat",
    .x == "Very confident" |
      .x == "Very committed" ~ "Very",
    TRUE ~ NA
  )))

```{r}
#| label: fns
#| include: false

source(here::here('src', 'funs.R'))

## Demographics

```{r}
#| label: tbl-1
#| tbl-cap: "Description of Sample Demographics"
#| tbl-cap-location: top

@@

## Summary Tables

```{r}
#| label: tbl-tc
#| tbl-cap: "Trust and Confidence in Election Administration"

# Likert table summary of Trust and confidence variables
tbl_tc <- data |> 
  select(q19:q24) |>
  gtsummary::tbl_likert(
    statistic = ~"{n} ({p}%)", 
    label = list(q19 = "Votes will be counted as intended",
                 q20 = "Election officials will do good job",
                 q21 = "Election workers will be committed",
                 q22 = "Voting process will be fair",
                 q23 = "Voting outcome will be fair",
                 q24 = "Election technology will be secure"))

# add continuous summary of Likert scores. Merge tables into one
tbl_tc_summary <- list(
  tbl_tc,
  gtsummary::tbl_wide_summary(
    data |>
      select(q19:q24) |> mutate(across(where(is.factor), as.numeric)),
    statistic = c("{mean}", "{sd}"),
    label = list(
      q19 = "Votes will be counted as intended",
      q20 = "Election officials will do good job",
      q21 = "Election workers will be committed",
      q22 = "Voting process will be fair",
      q23 = "Voting outcome will be fair",
      q24 = "Election technology will be secure"
    ),
    type = ~ "continuous"
  )
) |>
  gtsummary::tbl_merge(tab_spanner = F) |> 
  gtsummary::modify_header(label="")

# print as huxtable and modify using `huxtable` R package
gtsummary::as_hux_table(tbl_tc_summary) |>
  huxtable::set_width(0.6) |> 
  huxtable::set_col_width(rep(c(0.4))) |> 
  huxtable::theme_article() |> 
  huxtable::set_position("center")

```{r}
#| label: tbl-eef
#| tbl-cap: "Expectation of Electoral Fraud"

# Likert table summary of Expectation of electoral fraud :::::::::::::::::::####
tbl_eef <- data |> 
  select(contains("q28_")) |>
  gtsummary::tbl_likert(
    statistic = ~"{n} ({p}%)", 
    label = list(q28_1 = "There will be voter fraud",
                 q28_2 = "Many votes will not be counted",
                 q28_3 = "Voters will be turned away",
                 q28_4 = "Foreign Interference",
                 q28_5 = "Election officials will discourage some voters"))

# add continuous summary of Likert scores
tbl_eef_summary <- list(
  tbl_eef,
  gtsummary::tbl_wide_summary(
    data |>
      select(contains("q28_")) |> mutate(across(where(is.factor), as.numeric)),
    statistic = c("{mean}", "{sd}"), 
    label = list(q28_1 = "There will be voter fraud",
                 q28_2 = "Many votes will not be counted",
                 q28_3 = "Voters will be turned away",
                 q28_4 = "Foreign Interference",
                 q28_5 = "Election officials will discourage some voters"),
    type = ~ "continuous"
  )
) |>
  gtsummary::tbl_merge(tab_spanner = F) |> 
  gtsummary::modify_header(label="")

# print as huxtable and modify using `huxtable` R package
gtsummary::as_hux_table(tbl_eef_summary) |>
  huxtable::set_width(0.6) |> 
  huxtable::set_col_width(rep(c(0.4))) |> 
  huxtable::theme_article() |> 
  huxtable::add_footnote(border = 0.8,
    "Note: Full survey question and statement wording can be found in the appendix") |> 
  huxtable::set_position("center")

```{r}
#| label: tbl-safe
#| tbl-cap: "Concern for voter safety"

# Likert table summary of Concerns for Voter Safety ::::::::::::::::::::::::####
tbl_safe <- data |> 
  select(q25, q26) |>
  gtsummary::tbl_likert(
    statistic = ~"{n} ({p}%)", 
    label = list(q25 = "Potential for violence, threats, or intimidation",
                 q26 = "Polling sites will be safe for voters"))

# add continuous summary of Likert scores
tbl_safe_summary <- list(
  tbl_safe,
  gtsummary::tbl_wide_summary(
    data |>
      select(q25, q26) |> mutate(across(where(is.factor), as.numeric)),
    statistic = c("{mean}", "{sd}"),  
    label = list(q25 = "Potential for violence, threats, or intimidation",
                 q26 = "Polling sites will be safe for voters"),
    type = ~ "continuous"
  )
) |>
  gtsummary::tbl_merge(tab_spanner = F) |> 
  gtsummary::modify_header(label="**Concern**")

# print as huxtable and modify using `huxtable` R package
gtsummary::as_hux_table(tbl_safe_summary) |>
  huxtable::set_width(0.6) |> 
  huxtable::set_col_width(rep(c(0.4))) |> 
  huxtable::theme_article() |> 
  huxtable::add_footnote(border = 0.8,
    "Note: Full survey question and statement wording can be found in the appendix") |> 
  huxtable::set_position("center")

## Crosstables

@@

# Crosstab of Q19 by treatment group
data |> 
  janitor::tabyl(group, q19, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q19') |>
  gt::gt(
    rowname_col = 'Q19',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q19') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q19. Vote Count Confidence for Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q19. How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

@@

data |> 
  janitor::tabyl(group, q21, show_na = F) |> 
  # janitor::adorn_totals("both") |> 
  janitor::adorn_percentages("row") |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |>
  janitor::adorn_ns("rear") |> 
  janitor::adorn_title("combined", 
                       row_name = "Group",
                       col_name = "Q21") |>
  # bind_rows(.id = "group_var") |>   
  gt::gt(
    rowname_col = "row_var",
    groupname_col = "group_var") |>   
  gt::cols_label(
    c('Group/Q21') ~ "Group") |>
  # gt::cols_label_with(columns = '...1', fn = ~sjlabelled::get_label(df$q5.clps)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q21. Election staff commitment to fairness and accuracy"
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q21. Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ. How committed do you think they will be to making sure the elections held this November are fair and accurate?",
    locations = gt::cells_column_spanners()) |>
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )
